%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                          Curriculum Vitae Template Latex Code                  %
%                                                                                %
%                              Author: Manuel Pasqual Paul                       %
%                      Email: paul.manuel.pasqual@gmail.com                      %
%                                                                                %
%                             Last Edited: January 2020                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Specifications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article}
\usepackage{anysize}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{marvosym}
\usepackage{fontawesome5}
\usepackage[usenames,dvipsnames]{color}
\usepackage[left=0.5in,right=0.75in,top=1in,bottom=1in]{geometry}
\usepackage{ifthen}
\usepackage [autostyle, english = american]{csquotes}
\newcommand{\etal}{{et al.}}
\MakeOuterQuote{"}
\newboolean{noshad}
% \usepackage{blackrule}
\setboolean{noshad}{false} % Set to false to omit the author section
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Name & Contact Info %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\Large \bfseries Ali BaniAsad} \\
	\vspace{4pt}
	{\large Curriculum Vitae}
\end{center}

	% {\noindent \bf Contact Information} \\ [8pt]
	% \href{https://alibaniasad1999.github.io/}{\faGlobe} Website:
	% \href{https://alibaniasad1999.github.io/}{alibaniasad1999.github.io}
	% \\
	% \href{mailto:alibaniasad1999@yahoo.com}{\faEnvelope} Email: \href{mailto:alibaniasad1999@yahoo.com}{alibaniasad1999@yahoo.com}   \\
	% \href{https://linkedin.com/in/alibaniasad1999/}{{\faLinkedin}}
	% LinkedIn: \href{https://linkedin.com/in/alibaniasad1999/}{alibaniasad1999}
 % \\
	% \href{https://scholar.google.com/citations?user=KeKpSvEAAAAJ&hl=en}{\faGraduationCap} Scholar: \href{https://scholar.google.com/citations?user=KeKpSvEAAAAJ&hl=en}{alibaniasad1999} \\
	% \href{https://github.com/alibaniasad1999}{\faGithub}
	% GitHub: \href{https://github.com/alibaniasad1999}{alibaniasad1999}





\begin{multicols}{2} % Start a two-column environment
    \noindent \href{https://alibaniasad1999.github.io/}{\faGlobe} Website: \href{https://alibaniasad1999.github.io/}{alibaniasad1999.github.io} \\
    \href{https://scholar.google.com/citations?user=KeKpSvEAAAAJ&hl=en}{\faGraduationCap} Scholar: \href{https://scholar.google.com/citations?user=KeKpSvEAAAAJ&hl=en}{Ali BaniAsad}
    \\
    \href{https://linkedin.com/in/alibaniasad1999/}{{\faLinkedin}}
	LinkedIn: \href{https://linkedin.com/in/alibaniasad1999/}{alibaniasad1999}
    \\
    \href{https://github.com/alibaniasad1999}{\faGithub}
	GitHub: \href{https://github.com/alibaniasad1999}{alibaniasad1999}\\
	\href{mailto:alibaniasad1999@yahoo.com}{\faEnvelope} Email: \href{mailto:alibaniasad1999@yahoo.com}{alibaniasad1999@yahoo.com}   \\
	\faPhone \hspace{0pt}
	Phone: (+98) 991-214-7276
\end{multicols} % End the two-column environment

	% \faPhone \hspace{0pt}
	% Phone: (+98) 991-214-7276

%	Reza Pordal recently graduated with an M.Sc. in Aerospace Engineering from the Sharif University of Technology in Iran. His main research interest is in autonomous systems, with a particular focus on addressing environmental challenges and developing safe and robust control systems.
	\noindent\rule[0.5ex]{\linewidth}{.1pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{8pt}
\begin{center} % Begin Text Centering
	{\noindent \bfseries EDUCATION}
\end{center} % End Text Centering

 \vspace{-4pt} % Gap between title and text

\noindent
 \bf{M.S.}
 \normalfont{Aerospace Engineering} \hfill September 2022 -- April 2025 \\
\noindent \textit{Sharif University of Technology} \\

\noindent
 \bf{B.S.}
\normalfont{Aerospace Engineering} \hfill September 2017 -- May 2022 \\
\noindent \textit{Sharif University of Technology} \\
%{\setlength{\parindent}{1.1in}
%	{\indent \sl \bfseries Honors} \\
%	\indent [HONOR ITEM] \\
%	\indent [HONOR ITEM]}

%\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTEREST %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{center}
% 	{\noindent \bfseries 1  2}
% \end{center}

% \vspace{8pt} % Gap between title and text
% \setlength{\parindent}{0.5in}

% \indent
% [INSERT TEXT HERE] \\

% \vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTERSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-8pt}
\begin{center}
	{\noindent \bfseries RESEARCH INTERESTS}
\end{center}


% \vspace{6pt}
% \begin{multicols}{2} % Two-column layout
% 	\centering
% \begin{itemize} % No \itemsep for tighter spacing
% 	\item \textbf{\noindent Robotics}
% 	\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
% 	    \item \textbf{Reinforcement Learning}
% 	    \begin{itemize}
% 	        \item Multi-Agent Systems
% 	        \item Optimal Control in RL
% 	        \item Policy Optimization
% 	    \end{itemize}
% 	    % \item \textbf{Computer Vision}
% 	    % \begin{itemize}
% 	    %     \item Object Detection
% 	    %     \item Sensor Fusion
% 	    %     \item Image Segmentation
% 	    %     \item 3D Reconstruction
% 	    % \end{itemize}
% 	\end{itemize}
% 	\item \textbf{Artificial Intelligence}
% 	\begin{itemize} \itemsep -1pt
% 	    \item Machine Learning
% 	    \item Artificial Neural Networks
% 	    \item Deep Learning
% 	    \item Natural Language Processing
% 	\end{itemize}
% 	\item \textbf{Control Systems}
% 	\begin{itemize} \itemsep -1pt
% 	    \item Optimal Control
% 	    \item Automatic Control
% 	    \item Robust Control
% 	\end{itemize}
% 	\item \textbf{Game Theory}
% 	\begin{itemize} \itemsep -1pt
% 	    \item Differential Game
% 	    \item Multi-Agent Game
% 	    \item Cooperative Game Theory
% 	    \item Non-Cooperative Game Theory
% 	\end{itemize}
% \end{itemize}
% \end{multicols}
\begin{multicols}{3}
	\begin{itemize}\itemsep -2pt
		\item Reinforcement Learning
		\item Robotics
		\item Multi-Agent Systems
		\item Automatic Control
		% \item Optimization
		% \item Machine Learning
		% \item Deep Learning
		\item Game Theory
		\item Embedded ML
	\end{itemize}
\end{multicols}



%\vspace{0.1in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MENTORING EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newpage
\begin{center}
	{\noindent \bfseries PUBLICATIONS}
\end{center}

%\vspace{4pt} % Gap between title and text


\noindent
{\bfseries Journal Papers}
%\vspace{6pt}


\begin{itemize} \itemsep -2pt % Reduce space between items
	% \item Alireza Sharifi, \textbf{A BaniAsad}, \etal,
 % "Robust In-Motion Transfer Alignment of Low-Grade Inertial Navigation Systems with Recurrent Neural Networks in the Event of Reference Malfunction." \textit{Engineering Applications of Artificial Intelligence}, 2025
	% (\href{https://github.com/alibaniasad1999/INS_AI/blob/main/Report/revised.pdf}{\textcolor{blue}{minor review}}).
	\item A. Sharifi, \textbf{A. BaniAsad}, et al., "Robust In-Motion Transfer Alignment of Low-Grade Inertial Navigation Systems with Recurrent Neural Networks in the Event of Reference Malfunction," \textit{Engineering Applications of Artificial Intelligence}, 2025 (Submitted - Revised)
(\href{https://github.com/alibaniasad1999/INS-AI}{\textcolor{blue}{Project Repo (Code, Report) on GitHub}}).
	% (\href{https://github.com/alibaniasad1999/INS_AI/blob/main/Report/revised.pdf}{\textcolor{blue}{Submitted - Revised}}).
	\item \textbf{A. BaniAsad}, et al., "Attitude Control of a 3-DoF Quadrotor Platform Using a Linear Quadratic Integral Differential Game Approach," \textit{ISA Transactions}, vol. 148, pp. 515-527, 2024, doi: \href{https://doi.org/10.1016/j.isatra.2024.03.005}{10.1016/j.isatra.2024.03.005}.
	% AHRS AI when there is no AI
\end{itemize}

%\vspace{0.1in} % Some whitespace between sections
\noindent
{\bfseries Conference Papers}

%\vspace{4pt}
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item \textbf{A. BaniAsad} and H. Nobahari, "Robust DDPG Reinforcement Learning Differential Game Guidance in Low-Thrust, Multi-Body Dynamical Environments," in \textit{Proc. of 23rd International Conference of Iranian Aerospace Society}, 2025 (Accepted) (\href{https://github.com/alibaniasad1999/DGDDPG}{\textcolor{blue}{Project Repo (Code, Report) on GitHub}}).
    \item M. Amirpour, \textbf{A. BaniAsad}, and H. Nobahari, "Reinforcement Learning-Based Controller Design for a Suspended Ball Plant," in \textit{Proc. of 23rd International Conference of Iranian Aerospace Society}, [Location, Date, if known], 2025 (Accepted).
   (\href{https://drive.google.com/file/d/18oinC3TNsnMand_cw5BN_Z3qxRAvds8u/view?usp=sharing}{\textcolor{blue}{Report}}).
    % Add Link Here if available
	\item H. Nobahari, \textbf{A. BaniAsad}, and A. Sharifi, "Linear Quadratic Integral Differential Game applied to the Real-time Control of a Quadrotor Experimental setup," \textit{Proc. of 2022 10th RSI International Conference on Robotics and Mechatronics (ICRoM)}, 2022, pp. 578-583, doi: \href{https://doi.org/10.1109/ICRoM57054.2022.10025263}{10.1109/ICRoM57054.2022.10025263}.
\end{itemize}

\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROFESSIONAL EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \newpage
%\vspace{-4pt}
\begin{center}
	{\noindent \bfseries RESEARCH EXPERIENCE} % TODO: make it short
\end{center}

\vspace{8pt} % Gap between title and text

\noindent

% \vspace{-4pt}
% \vspace{0.2in}
\noindent
{\bfseries  Embedded RL Control for Robots on Resource-Constrained Hardwares
\href{https://github.com/CNAVLAB}{\faGithub}
} \hfill Aug.\ 2022 -- Apr.\ 2025 \\[2pt]
\noindent \textit{Master's Thesis in Sharif University of Technology} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Nobahari Hadi, PhD} \ifthenelse{\boolean{noshad}}
{
	and
Mohammad Noshad, PhD
 }{}
\vspace{-4pt}
\begin{itemize}  \itemsep -2pt % Slightly reduced spacing for sub-items
	% \item Investigated \textbf{Deep Reinforcement Learning} methods, comparing their performance with classical strategies, such as \textbf{MPC}, to identify strengths and weaknesses.
	% \item Integrated \textbf{ROS} to test and validate robotic \textbf{Embedded RL} in \textbf{Real-World} scenarios.
	% \item Utilized \textbf{Game Theory} to develop \textbf{Robust} and \textbf{Safe}
	% \textbf{Multi-Agent}
	%  RL algorithms.
	\item Outperformed classical MPC, cutting trajectory-tracking error by 22 \% within strict on-board CPU/memory limits.
	\item Designed zero-sum, disturbance-augmented training that kept policies stable under $10\times$ worst-case perturbations.
	\item Engineered 15 k-LOC RL control stack (DDPG, TD3, SAC, PPO) in PyTorch/TensorFlow+Gym for embedded robots.
    \item Validated robustness on Gymnasium locomotion tasks—Ant, Humanoid, HalfCheetah, Walker2d.%
    \item Ported the system to a C++/Python ROS 2 hardware-in-the-loop node for on-board testing.%
    \item Open-sourced full code, LaTeX report, and Jupyter demos to enable one-command reproduction for future researchers.
	% \item Simulated and evaluated the \textbf{robustness} of proposed methods, demonstrating their effectiveness in maintaining \textbf{safety} and \textbf{optimizing} performance under \textbf{dynamic constraints}.
\end{itemize}
\noindent
{\bfseries Researcher at
\href{https://www.linkedin.com/company/cnav-lab/}{\textcolor{blue}{CNAV Lab \faLinkedin}} \href{https://github.com/CNAVLAB}{\faGithub}
\textcolor{red}{
\href{https://youtube.com/@cnavlab?si=Fc-Y3oyKdgAmz3-5}{\faYoutube}}
} \hfill May\ 2020 -- Feb.\ 2025 \\[2pt]
\noindent \textit{Head of Lab (Current), Researcher (Former)}
\hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Nobahari Hadi, PhD} and
\href{https://ae.sharif.edu/~portal/faculty/1730782165}{Sharifi Alireza, PhD}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Led projects on \textbf{Embedded AI} in C, \textbf{Reinforcement Learning (RL)}, and \textbf{ROS} for robotic control systems.
	\item Designed \textbf{RL} algorithms to enhance robotic \textbf{navigation}, \textbf{decision-making}, and adaptability.
    \item Robust in-motion Transfer Alignment method based on the multilayer Neural Network. \href{https://github.com/alibaniasad1999/INS-AI}{\faGithub}
\vspace{-6pt}
    \begin{itemize}
    \item Proposed \textbf{LSTM–MLP} that performs in-motion using only IMU + SINS data when GPS is unavailable.
    \item Cuts navigation drift to \(\!<0.1\%\) of the Kalman-INS error during 100 s GPS outages.
    \item Generalises across ship, ROV, and car datasets, outperforming conventional methods out of domain.
    \end{itemize}
    % \item Validated AI navigation in \textbf{real-world} applications to ensure \textbf{robustness} and \textbf{reliability}.
\end{itemize}

% \vspace{-4pt}
% \vspace{0.2in}
\noindent
{\bfseries Game Theory-Based Control for Three Degrees of Freedom Platform
\href{https://github.com/alibaniasad1999/bachelor-thesis}{\faGithub}
\textcolor{red}{
\href{https://youtu.be/SXZACxGaE1A?si=61yCRB8jFIZlldFG}{\faYoutube}}
} \hfill Feb.\ 2021 -- Sep.\ 2023 \\[2pt]
\noindent \textit{Bachelor's Thesis in Sharif University of Technology} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Nobahari Hadi, PhD} \\[2pt]
{\footnotesize \textbf{\textit{Awarded the Best Undergraduate Thesis \faMedal}}}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Slightly reduced spacing for sub-items
 %    \item Developed a robust \textbf{Robot} control system using \textbf{Differential Game Theory}.
	% % , applying \textbf{Nash equilibrium} to solve the game and optimize performance under \textbf{uncertainty}.
	%  % parameter estimation of quad
	%  \item employed \textbf{Optimization} for \textbf{System Identification}, enhancing control \textbf{Reliability}.
 %    % \item Evaluated system performance via \textbf{simulations}, ensuring the validity of theoretical \textbf{model}.
 %    \item Tested the control strategy on a \href{https://gcrc.sharif.edu/استند-آزمایشگاهی-کنترل-وضعیت-سه-درجه-آ/}{\textcolor{blue}{3DoF setup}}, demonstrating the \textbf{Game-Theoretic} approach.
    % \item Conducted experiments to assess the setup's \textbf{stability}, refining algorithms based on feedback.
    \item Modelled a \href{https://gcrc.sharif.edu/استند-آزمایشگاهی-کنترل-وضعیت-سه-درجه-آ/}{\textcolor{blue}{3-DoF setup}} in Simulink and identified dynamics for parameter estimation.
    \item Controlled a \href{https://gcrc.sharif.edu/استند-آزمایشگاهی-کنترل-وضعیت-سه-درجه-آ/}{{3-DoF quadcopter stand}} using \textbf{Differential Game} theory and \textbf{Nash Equilibrium} for robust control.
    \item Implemented the controller through a MATLAB/Simulink–to–C pipeline for real-time hardware tests.
    \item Benchmarked against \textbf{ADRC} and \textbf{DOBC}, achieving superior disturbance rejection and robustness.

\end{itemize}

% \vspace{-4pt}
% \vspace{0.2in}

\noindent
{\bfseries Coordination of Multi-Agent Autonomous Systems
\href{https://github.com/alibaniasad1999/Coordination-of-Multi-Agent-Autonomous-Systems}{\faGithub}
} \hfill July 2023 \\[2pt]
\noindent \textit{Project in Sharif University of Technology} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Nobahari Hadi, PhD}
% \\
% {\footnotesize \textbf{\textit{Top Score Project \faMedal}}}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Slightly reduced spacing for sub-items
    % \item Developed and optimized a swarm model, addressing \textbf{communication delays} and \textbf{obstacle avoidance}.
	\item Optimized a \textbf{Multi-Agent} model for \textbf{Communication Delays} and \textbf{Obstacle Avoidance}.
	
    \item Implemented and validated the model with \textbf{Simulink} simulations and \textbf{HIL} testing using \textbf{Embedded C} on a \textbf{Microcontroller}, ensuring robustness and reliability.
	% \item Developed and optimized a \textbf{swarm} model for flocking behavior, addressing \textbf{communication delays} and environmental obstacles, then validated it through Simulink simulations and \textbf{HIL} testing with \textbf{embedded C} on a \textbf{microcontroller} to ensure robustness and reliability.
\end{itemize}

% \vspace{-4pt}
% \vspace{0.2in}
\noindent
{\bfseries Multi-Objective Heuristic Optimization
\href{https://github.com/alibaniasad1999/Heuristic-optimization-algorithms}{\faGithub}
}
\hfill February 2023 \\[2pt]
\noindent \textit{Project in Sharif University of Technology} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Nobahari Hadi, PhD}
% \\
% {\footnotesize \textbf{\textit{Top Score Project \faMedal}}}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Slightly reduced spacing for sub-items
    \item Implemented the \href{https://link.springer.com/article/10.1007/s12652-022-04332-8}{\textcolor{blue}{REMARK}} algorithm for \textbf{Multi-Objective Optimization} with \textbf{Conflicting} objectives, allowing for the effective evaluation of trade-offs.
    \item Utilized \textbf{heuristic} methods to achieve high approximations of the \textbf{Pareto set}, balancing multiple objectives for optimal decision-making.
\end{itemize}
% \vspace{-4pt}
% \vspace{0.2in}
\noindent
{\bfseries Advanced Aircraft Trim Stability Analysis
\href{https://github.com/alibaniasad1999/DATCOM-Trim-Diagram-GUI}{\faGithub}
}
\hfill March 2022 \\[2pt]
\noindent \textit{Project in Sharif University of Technology} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{http://ae.sharif.edu/~portal/faculty/1014037799}{Afshin Banazadeh, PhD}
% \\
% {\footnotesize \textbf{\textit{My Top Star Repository \faStar}}}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Slightly reduced spacing for sub-items
    \item Developed an advanced \textbf{User Interface} software, enhancing aircraft  \textbf{Stability Analysis}.
    \item  \textbf{Real-Time} visualization and \textbf{Interactive} adjustments for aircraft performance \textbf{Evaluation}.
    % \item Validated the UI for reliability, \textbf{optimizing} the \textbf{design process} for engineers and researchers.
\end{itemize}

% \vspace{-4pt}
% \vspace{0.2in}
\noindent
{\bfseries AIAA Regional Jet Design Competition
\href{https://github.com/alibaniasad1999/Airplane-Design-II}{\faGithub}
}
\hfill June 2021 \\[2pt]
\noindent \textit{Project in Sharif University of Technology
\color{blue}{[\href{https://github.com/alibaniasad1999/CV/blob/main/attachments/PhoenixTeamModernRegionalJet.jpg}{Poster of the Aircraft}]}
} \hfill Tehran, Iran \\[2pt]
\noindent Supervisors:
\href{http://ae.sharif.edu/~portal/faculty/1014037799}{Afshin Banazadeh, PhD}
% \\
% {\footnotesize \textbf{\textit{Top Group Project for Two Semesters \faMedal}}}
\vspace{-4pt}
\begin{itemize} \itemsep -2pt % Slightly reduced spacing for sub-items
    \item Led regional jet design, integrating  disciplines for \textbf{Performance} and \textbf{Industry Standards}.
	\item Developed a project \href{https://drive.google.com/drive/folders/1nyzjUDzIgUuoJlB1KRaJeTH69p20cMUK?usp=sharing}{\textcolor{blue}{report}} and presentation, highlighting \textbf{Design Choices} and simulation results, leading to a successful team presentation.
    \item Applied \textbf{ computer modeling}  for aerodynamic, structural, and performance analysis.
    \item Developed an \textbf{automated design cycle} that allows for seamless updates across all stages.
\end{itemize}




\begin{center}
	{\noindent \bfseries TEACHING EXPERIENCE}
\end{center}
% \vspace{-4pt}
\noindent\textbf{Section Leader — Stanford University}\hfill Apr 2025 -- Present
\begin{itemize}
  \setlength\itemsep{0pt}
  \vspace{-4pt}
  \item Code in Place (CS106A)
  \item Mentored 20 international learners in Python. % completed final project
\end{itemize}
\vspace{-4pt}
% ---------- Sharif TA ----------------------------------
\noindent\textbf{Teaching Assistant — Sharif University of Technology}\hfill Sep 2018 – Present
\begin{itemize}
  \setlength\itemsep{0pt}       % no extra package needed
  \vspace{-4pt}
  \item Automatic Control (2021 – Present)
  \item Control Lab (2022 – Present)
  \item Dynamics (Jan 2023 – Dec 2023)
  \item Aircraft Design II (Fall 2021)
  \item Fundamentals of Programming (C/C++) (Fall 2018)
\end{itemize}
\vspace{-4pt}
\noindent\textbf{Community Outreach} \hfill Sep 2020 -- Dec 2021
\vspace{-4pt}
\begin{itemize}
  \setlength\itemsep{0pt}
%   \vspace{-4pt}
  \item University Entrance-Exam Preparation, %
  \href{https://www.instagram.com/virgool_charity?igsh=MWxsOGF3cTk1dzY3dw==}{\textcolor{blue}{Virgol Charity}}.%
\end{itemize}


% \vspace{0.2in} % Some whitespace between sections%


\begin{center}
	{\noindent \bfseries AWARDS AND HONORS}
\end{center}


% \vspace{8pt} % Gap between title and text


% \noindent
% {\bfseries Iranian Aerospace Society's Best Undergraduate Thesis Award}
% \hfill 2023 \vspace{4pt} \\
% % TODO: add link
% \textit{Awarded for the exceptional
% undergraduate thesis titled "Control of a 3DOF Quadrotor Stand using a Linear-Quadratic-Integral Controller
% based on Differential Game Theory".}

% \vspace{04pt}
% \noindent
% {\bfseries Ranked 23}
% \hfill 2022 \vspace{4pt}\\
% \textit{Ranked 23 among more than thousands participants in the Nationwide University Entrance Exam for Aerospace Engineering.}
% \vspace{12pt}




% \vspace{04pt}
% \noindent
% {\bfseries Ranked Top 0.5\%}\hfill 2017 \vspace{4pt} \\
% \textit{Ranked Top 0.5\% among 150,000 participants of Iran's Undergraduate University Entrance Exam.}

% \vspace{04pt}
% \noindent
% {\bfseries Member of NODET}\hfill 2010 -- 2017 \vspace{4pt} \\
% \textit{
% 	Recognized as an Exceptional Talent by Iran's National Elites Foundation, a National Organization Dedicated to the Development of Exceptionally Talented individuals (\textit{\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{\textcolor{blue}{NODET}}}).
% }


% ------------------ Awards & Honors ------------------
% \noindent\textbf{Awards \& Honors}

\begin{itemize} \itemsep -2pt  % enumitem
  \item Best Undergraduate Thesis — Iranian Aerospace Society (2023)\\
        \textit{“Control of a 3-DOF Quadrotor Stand via LQI \& Differential Game Theory”}
  \item National M.Sc.\ Entrance Exam (Aerospace) — Rank 23 / 1 000+ (2022)
  \item National B.Sc.\ Entrance Exam — Top 0.5 \% of 150 000 (2017)
  \item \href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{\textcolor{blue}{NODET}} Scholar — National Organization for Development of Exceptional Talents (2010–2017)
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%% VOLUNTEER EXPERIENCE & CAUSES %%%%%%%%%%%%%%%%%%%%%%%%%%

% \newpage


% {\bfseries Teaching Assistant}
% \begin{itemize}
% 	% \item
% 	\item {\bfseries Code in Place (Stanford CS106A)}
%      \hfill April 2025 -- Ongoing \\
%     \textit{Stanford University (Online Program)}\\
%     Course developed by Stanford team including Nick Parlante and Eric Roberts.
% 	\item {\bfseries Automatic Control}
% 	 \hfill September 2021 -- Present \\
% 	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
% 	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Nobahari Hadi}}, PhD and \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Sharifi Alireza}, PhD}
% 	\item {\bfseries Control Lab}
% 	 \hfill September 2021 -- Present \\
% 	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
% 	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Nobahari Hadi}}, PhD and \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Sharifi Alireza}, PhD}
% 	\item {\bfseries Dynamics}
% 	 \hfill September 2021 -- December 2023 \\
% 	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
% 	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Sharifi Alireza}}, PhD
% 	\item {\bfseries Aircraft Design II}
% 	\hfill September 2021 -- December 2021 \\
%    \textit{Department of Aerospace Engineering, Sharif University of Technology}\\
%    Instructors: \href{http://ae.sharif.edu/~portal/faculty/1014037799}{\textcolor{blue}{Banazadeh Afshin}} PhD
% 	\item \noindent{\bfseries Fundamentals of Programming (C/C++)}
% 	\hfill September 2018 -- December 2018 \\
%    \textit{Department of Computer Engineering, Sharif University of Technology}\\
%    %  \hfill [September 2017] \\
%    \noindent Instructor: \href{https://www.linkedin.com/in/marjan-nikbin-a27451111}{\textcolor{blue}{Nikbin Marjan}}


% \end{itemize}

% \noindent{\bfseries Volunteer Teaching}
% \begin{itemize}
% 	\item {\bfseries University Entrance Exam Preparation}
% 	\hfill September 2020 -- December 2021 \\
% 	\textit{\href{https://www.instagram.com/virgool_charity?igsh=MWxsOGF3cTk1dzY3dw==}{\textcolor{blue}{Virgol}} Charity, Local Community} \\
% 	Provided educational support to underprivileged children as part of a local charity initiative.
% \end{itemize}


% % --- Teaching & Mentorship -----------------------------------------------
% \noindent{\bfseries Teaching \& Mentorship}

% \begin{itemize}
%   \item {\bfseries Teaching Assistant} — Sharif University of Technology%
%   \hfill Sep 2018 -- Present\\
%         Courses: Automatic Control (2021 -- Present) · Control Lab (2022 -- Present) ·
%         Dynamics (2023 -- 2023) · Aircraft Design II (Fall 2021) ·
%         Fundamentals of Programming (C/C++) (Fall 2018)

%   \item {\bfseries Section Leader} — Code in Place (CS106A), Stanford University%
%   \hfill Apr 2025 -- Present
% \end{itemize}

% \vspace{4pt}
% \noindent{\bfseries Volunteer Tutor} — University Entrance-Exam Preparation, %
% \href{https://www.instagram.com/virgool_charity?igsh=MWxsOGF3cTk1dzY3dw==}{\textcolor{blue}{Virgol Charity}}%
% \hfill Sep 2020 -- Dec 2021






% ---------------- Teaching & Mentorship -----------------
% ---------------- Teaching & Mentorship -----------------
% \section*{Teaching \& Mentorship}


% ---------- Stanford ------------------------------------
% \textbf{Section Leader — Code in Place (CS106A), Stanford University}\hfill Apr 2025 – Present

% \begin{itemize}
%   \setlength\itemsep{2pt}
%   \item Mentored 65 international learners in Python; 97 % completed final project
% \end{itemize}

% % ---------- Outreach ------------------------------------
% \textbf{Volunteer Tutor — University Entrance-Exam Prep, Virgol Charity}\hfill Sep 2020 – Dec 2021

% % ---------- Stanford ------------------------------------
% \textbf{Section Leader — Code in Place (CS106A)}\\
% Stanford University\hfill Apr 2025 -- Present

% \begin{itemize}
%   \setlength\itemsep{2pt}
%   \item Mentored 65 international learners in Python; 97 % completed final project
% \end{itemize}

% ---------- Outreach ------------------------------------





% \vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HONORS & MEMBERSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



% \vspace{12pt}
% \noindent
% {\bfseries Admittance in the entrance exam of {\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{\textcolor{blue}{NODET}}} high school.}\hfill 2013 \\
% TODO: add link
% among 150,000 participants of Iran's Undergraduate University Entrance Exam



% \vspace{0.2in} % Some whitespace between sections

% \newpage
% \newpage
\begin{center}
	{\noindent \bfseries TECHNICAL SKILLS}
\end{center}
\vspace{-8pt}
% \begin{itemize}
% 	\small{\item{
% \textbf{Programming Languages}{: C/C++, Embedded C, MATLAB, Python \faPython} \\
% \textbf{Tools and Platforms}{: Git \faGit*, Linux \faLinux, ROS, Simulink, \faTerminal  Terminal,  \LaTeX} \\
% \textbf{Libraries/Frameworks}{: Matplotlib, NumPy, Pandas, PyTorch, TensorFlow} \\
% \textbf{Quantitative Skills}{: Artificial Neural Networks, Data Structures, Deep Learning, Embedded Machine Learning, Heuristic Optimization, Image Processing, Machine Learning, Optimization, Reinforcement Learning, Robotics}

% 			\textbf{Languages}{: Farsi (Native), English (Full Professional Proficiency)} \\
% 	}}
% \end{itemize}


% \begin{itemize}
%         \item \textbf{Programming Languages:} C/C++, Embedded C, MATLAB,
% \end{itemize}

% Python \faPython \\
%         \textbf{Tools and Platforms:} Git \faGit, Linux \faLinux, ROS, Simulink, \faTerminal Terminal, \LaTeX \\
%         \textbf{Libraries/Frameworks:} Matplotlib, NumPy, Pandas, PyTorch, TensorFlow \\
%         \textbf{Quantitative Skills:} Artificial Neural Networks, Data Structures, Deep Learning, Embedded Machine Learning, Heuristic Optimization, Image Processing, Machine Learning, Optimization, Reinforcement Learning, Robotics \\
%         \textbf{Languages:} Farsi (Native), English (Full Professional Proficiency)
\vspace{-8pt}
\begin{itemize} \itemsep -12pt
	\item \textbf{Programming Languages:}
	\vspace{-8pt}
	\begin{multicols}{4}
		\begin{itemize}

			\item C/C++
			\item Embedded C
			\item MATLAB
			\item Python \faPython
		\end{itemize}
	\end{multicols}
	\item \textbf{Tools and OS:}
	\vspace{-8pt}
	\begin{multicols}{3}
		\begin{itemize}
			\item Git \faGitSquare
			\item Linux \faLinux
			\item ROS
			\item Simulink
			\item Terminal \faTerminal
			\item \LaTeX
		\end{itemize}
	\end{multicols}
	% \begin{itemize}
	% 	\item Git \faGit
	% 	\item Linux \faLinux
	% 	\item ROS
	% 	\item Simulink
	% 	\item Terminal \faTerminal
	% 	\item \LaTeX
	% \end{itemize}
	\item \textbf{Libraries/Frameworks:}
	\vspace{-8pt}
	\begin{itemize}
		\item \textbf{Machine Learning Libraries:}\\
		PyTorch, TensorFlow, Keras, Scikit-learn, OpenCV, OpenAI Gym, JAX
		% \begin{multicols}{2}
		% 	\begin{itemize}
		% 		\item PyTorch
		% 		\item TensorFlow
		% 		\item Keras
		% 		\item Scikit-learn
		% 		\item OpenAI Gym
		% 		\item JAX
		% 	\end{itemize}
		% \end{multicols}
		% \begin{itemize}
		% 	\item PyTorch C and Python
		% 	\item TensorFlow C and Python
		% 	\item Keras
		% 	\item Scikit-learn
		% 	\item OpenAI Gym
		% \end{itemize}

		\item \textbf{Data Analysis and Visualization Libraries:}\\
		Matplotlib, NumPy, Pandas, Seaborn, Plotly
		% \begin{multicols}{4}
		% 	\begin{itemize}
		% 		\item Matplotlib
		% 		\item NumPy
		% 		\item Pandas
		% 		\item OpenCV
		% 	\end{itemize}
		% \end{multicols}
		% \begin{itemize}
		% 	\item Matplotlib
		% 	\item NumPy
		% 	\item Pandas
		% 	\item OpenCV
		% \end{itemize}

		\item \textbf{Simulation Tools:}
		Gazebo, MuJoCo
		% \begin{multicols}{2}
		% 	\begin{itemize}
		% 		\item Gazebo
		% 		\item MuJoCo
		% 	\end{itemize}
		% \end{multicols}
		% \begin{itemize}
		% 	\item Gazebo
		% 	\item MuJoCo
		% \end{itemize}
	\end{itemize}
	% \item \textbf{Robotics Skills}
	% \begin{itemize}
	% 	\item Machine Learning
	% 	\begin{multicols}{2}
	% 		\begin{itemize}
	% 			\item Deep Learning
	% 			\item Artificial Neural Networks
	% 			\item Recurrent Neural Networks
	% 			\item Embedded Machine Learning
	% 			\item Reinforcement Learning
	% 			\item Heuristic Optimization
	% 			\item Convex Optimization
	% 			\item Image Processing
	% 		\end{itemize}
	% 	\end{multicols}
	% 	% \begin{itemize}
	% 	% 	\item Deep Learning
	% 	% 	\item Artificial Neural Networks
	% 	% 	\item Recurrent Neural Networks (RNN)
	% 	% 	\item Embedded Machine Learning
	% 	% 	\item Reinforcement Learning
	% 	% 	\item Heuristic Optimization
	% 	% 	\item Optimization
	% 	% 	\item Image Processing
	% 	% \end{itemize}
	% 	\item Control Systems
	% 	\begin{multicols}{3}
	% 		\begin{itemize}
	% 			\item Optimal Control
	% 			\item Automatic Control
	% 			\item Robust Control
	% 		\end{itemize}
	% 	\end{multicols}
	% 	% \begin{itemize}
	% 	% 	\item Optimal Control
	% 	% 	\item Automatic Control
	% 	% 	\item Robust Control
	% 	% \end{itemize}
	% 	\item Game Theory
	% 	\begin{multicols}{2}
	% 		\begin{itemize}
	% 			\item Differential Game
	% 			\item Multi-Agent Systems
	% 			\item Cooperative Game
	% 			\item Non-Cooperative Game
	% 		\end{itemize}
	% 	\end{multicols}
		% \begin{itemize}
		% 	\item Game Theory
		% 	\item Differential Game Theory
		% 	\item Multi-Agent Systems
		% 	\item Multi-Agent Game
		% \end{itemize}
	% \end{itemize}

	% \begin{itemize}
	% 	\begin{itemize}
	% 		\item Robotics
	% 	\end{itemize}
	% \end{itemize}
	\vspace{4pt}
	\item \textbf{Languages:} Farsi (Native), English (Full Professional Proficiency) % add toefl score here
	\vspace{1pt} \\
	The TOEFL iBT score is 96 (Reading: 26, Listening: 27, Speaking: 22, Writing: 21)
	% \begin{itemize}
	% 	\item Farsi (Native)
	% 	\item English (Full Professional Proficiency) % add toefl score here
	% 	\vspace{1pt} \\
	% 	The TOEFL iBT score is 96 (Reading: 26, Listening: 27, Speaking: 22, Writing: 21)
	% 	% very little arabic
	% \end{itemize}
\end{itemize}

% \vspace{0.1in} % Some whitespace between sections




\begin{center}
	{\noindent \bfseries NOTABLE COURSES}
\end{center}

% \vspace{0.2in} % Some whitespace between sections

% \noindent
% {\bfseries University Courses}
% \hfill 2017 -- 2024\\
% \textit{Sharif University of Technology, Tehran, Iran}
% \begin{itemize}\itemsep -10pt
%     \item \textbf{Programming and Computational Methods:}\vspace{-4pt}
%     \begin{multicols}{2}\itemsep -4pt
%     \begin{itemize}
%         \item Basic Programming of C (20)
%         \item Numerical Calculations (20)
%     \end{itemize}
%     \end{multicols}

%     \item \textbf{Mathematics and Statistics:}\vspace{-4pt}
%     \begin{multicols}{1}
%     \begin{itemize}
%         \item Engineering Mathematics (19.8)
%         \item Probability and Statistics (20)
%     \end{itemize}
%     \end{multicols}

%     \item \textbf{Control Systems:}\vspace{-4pt}
%     \begin{multicols}{2}
%     \begin{itemize}
%         \item Automatic Control (18.1)
%         \item Control Lab (18.5)
%         \item Optimal Control (17.5)
%     \end{itemize}
%     \end{multicols}

%     \item \textbf{Aerospace Engineering:}\vspace{-4pt}
%     \begin{multicols}{2}
%     \begin{itemize}
%         \item Aircraft Design II (18.3)
%         \item Flight Dynamics II (18.3)
%     \end{itemize}
%     \end{multicols}

%     \item \textbf{Research and Projects:}\vspace{-4pt}
%     \begin{multicols}{2}
%     \begin{itemize}
%         \item Bachelor Thesis (20)
%     \end{itemize}
%     \end{multicols}
% \end{itemize}

% ------------ Selected University Courses -----------------
\noindent\textbf{Selected University Courses}%
\hfill \textit{Sharif University of Technology, Tehran} ~ (2017--2024)\\
\vspace{-8pt}
\begin{itemize} \itemsep -2pt  % enumitem package
  \item \textbf{Programming \& Numerics}: Basic C Programming (20), Numerical Calculations (20)
  \item \textbf{Math \& Statistics}: Engineering Mathematics (19.8), Probability \& Statistics (20)
  \item \textbf{Control Systems}: Automatic Control (18.1), Control Lab (18.5), Optimal Control (17.5)
  \item \textbf{Aerospace Engineering}: Aircraft Design II (18.3), Flight Dynamics II (18.3)
  \item \textbf{Research}: B.Sc.\ Thesis (20)
\end{itemize}


% \newpage
% \noindent
% {\bfseries Online Courses}
% \hfill 2017 -- 2024\\

% \begin{itemize} \itemsep -1pt
% 	\item \textbf{Robotics:}
% 	\hfill
% 	\href{https://coursera.org/share/169250f50fb50f44b803162274217f86}{\textcolor{blue}{verify certificate}}
% 	 \\
% 	\textit{Provided by University of Pennsylvania, Courser}
% 	\begin{multicols}{2}
% 		\begin{itemize}
% 			\item Aerial Robotics
% 			\item Computational Motion Planning
% 			\item Mobility
% 			\item Perception
% 			\item Estimation and Learning
% 			\item Capstone
% 		\end{itemize}
% 		\end{multicols}
% 	\item \textbf{Reinforcement Learning:}
% 	\hfill
% 	\href{https://www.coursera.org/account/accomplishments/specialization/LWJMD8VB28PZ?utm_source=link&utm_medium=certificate&utm_content=cert_image&utm_campaign=sharing_cta&utm_product=s12n}{\textcolor{blue}{verify certificate}}
% 	 \\
% 	\textit{Provided by University of Alberta, Coursera}
% 	% \begin{multicols}{1}
% 		\begin{itemize}
% 			\item Fundamentals of Reinforcement Learning
% 			\item Sample-based Learning Methods
% 			\item Prediction and Control with Function Approximation
% 			\item A Complete Reinforcement Learning System
% 		\end{itemize}
% 		\vspace{8pt}
% 		% \end{multicols}
% 	\item \textbf{IBM AI Engineering:} \\
% 	\textit{Provided by IBM, Coursera}
% 	\begin{itemize}
% 		\item Machine Learning with Python
% 		\item Introduction to Deep Learning and Neural Networks with Keras
% 		\item Building Deep Learning Models with TensorFlow
% 		\item Introduction to Neural Networks and PyTorch
% 		\item Introduction to Computer Vision and Image Processing
% 		\item AI Capstone Project with Deep Learning
% 	\end{itemize}
% 	\vspace{8pt}
% 	\item \textbf{Fundamentals of Accelerated Computing with CUDA Python:}
% 	\\
% 	\textit{Provided by NVIDIA}
% 	\item \textbf{Neural Networks and Deep Learning:}
% 	\hfill
% 	\href{https://coursera.org/share/8d9110917e9443857718534087a51190}{\textcolor{blue}{verify certificate}}
% 	\\
% 	\textit{Provided by deeplearning.ai, Coursera}
% 	\vspace{8pt}
% 	\item \textbf{Python Data Structures:}
% 	\hfill
% 	\href{https://coursera.org/share/8944f2b056a3405c606e509e61f5570e}{\textcolor{blue}{verify certificate}}
% 	\\
% 	\textit{Provided by University of Michigan, Coursera}
% 	\vspace{8pt}
% 	\item \textbf{Introduction to Embedded Machine Learning:}
% 	\hfill
% 	\href{https://coursera.org/share/0b709e9d6305db689ca5018f1531f4ef}{\textcolor{blue}{verify certificate}}
% 	\\
% 	\textit{Provided by Edge Impulse, Coursera}
% 	\vspace{8pt}
% 	\item \textbf{Game Theory:}
% 	\hfill
% 	\href{https://coursera.org/share/7c342a051890483df7748d65ad0113c2}{\textcolor{blue}{verify certificate}}
% 	\\
% 	\textit{Provided by Stanford University, Coursera}
% \end{itemize}


% ------------------ Online Courses ------------------
\noindent\textbf{Online Courses}\hfill 2017--2024\\
\vspace{-26pt}

\begin{itemize} \itemsep -2pt
  \item \textbf{Robotics Specialization} — Univ.\ of Pennsylvania\,
        (6 courses)\,
        \href{https://coursera.org/share/169250f50fb50f44b803162274217f86}{\textcolor{blue}{verify}}
  \item \textbf{Reinforcement Learning Specialization} — Univ.\ of Alberta\,
        (4 courses)\,
        \href{https://www.coursera.org/account/accomplishments/specialization/LWJMD8VB28PZ?utm_source=link&utm_medium=certificate&utm_content=cert_image&utm_campaign=sharing_cta&utm_product=s12n}{\textcolor{blue}{verify}}
  \item \textbf{AI Engineering Pro-Cert} — IBM\,
        (6 courses)
  \item \textbf{Accelerated Computing with CUDA Python} — NVIDIA
  \item \textbf{Neural Networks \& Deep Learning} — deeplearning.ai\,
        \href{https://coursera.org/share/8d9110917e9443857718534087a51190}{\textcolor{blue}{verify}}
  \item \textbf{Python Data Structures} — Univ.\ of Michigan\,
        \href{https://coursera.org/share/8944f2b056a3405c606e509e61f5570e}{\textcolor{blue}{verify}}
  \item \textbf{Intro to Embedded Machine Learning} — Edge Impulse\,
        \href{https://coursera.org/share/0b709e9d6305db689ca5018f1531f4ef}{\textcolor{blue}{verify}}
  \item \textbf{Game Theory} — Stanford University\,
        \href{https://coursera.org/share/7c342a051890483df7748d65ad0113c2}{\textcolor{blue}{verify}}
\end{itemize}



% \begin{center}
% 	{\noindent \bfseries HOBBIES}
% \end{center}
% \vspace{-8pt}
% \begin{multicols}{3}
% \begin{itemize} \itemsep -4pt
%     \item Violin \faMusic
%     \item Classical Music  \faHeadphones
%     \item Reading  \faBook
%     % \item Coding  \faLaptopCode
%     % \item Swimming \faSwimmer
%     % \item Hiking \faMountain
%     % \item Traveling \faPlane
%     % \item Photography \faCamera
%     % \item Chess \faChess
% \end{itemize}
% \end{multicols}



% \vspace{0.2in} % Some whitespace between sections


% % \newpage
% \begin{center}
% 	{\noindent \bfseries REFERENCES}
% \end{center}

% \ifthenelse{\boolean{noshad}}
% {
% 	\begin{itemize}
% 		\item \textbf{Noshad, Mohammad, PhD} \\
% 		Assistant Professor of Aerospace Engineering, Sharif University of Technology \\
% 	Dr. Noshad
% 		\begin{multicols}{2}
% 			\begin{itemize}
% 				\item \faGlobe \ \href{-5}{\textcolor{blue}{-}}
% 				\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=YJIJLs0AAAAJ&hl=en}{\textcolor{blue}{Google Scholar Profile}}
% 				\item \faEnvelope \ \href{mailto:moh@shyld.ai}{moh@shyld.ai}
% 				\item \faPhone \ +1 (669) 246-8140
% 			\end{itemize}
% 	\end{multicols}
% 	\end{itemize}
%  }{}


% \begin{itemize}
% 	\item \textbf{Sharifi, Alireza, PhD} \\
% 	Assistant Professor of Aerospace Engineering, Sharif University of Technology \\
% Dr. Sharifi Supervised my work in the \href{https://www.linkedin.com/company/cnav-lab/}{\textcolor{blue}{CNAV Lab}} for over three years, during which we collaborated on multiple projects.
% I served as both a researcher and a teaching assistant during this time.
% 	\begin{multicols}{2}
% 		\begin{itemize}
% 			\item \faGlobe \ \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Faculty Page at Sharif University}}
% 			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=k_OdlNMAAAAJ&hl=en}{\textcolor{blue}{Google Scholar Profile}}
% 			\item \faEnvelope \ \href{mailto:ar.sharifi@sharif.edu}{ar.sharifi@sharif.edu}
% 			\item \faPhone \ (+98)-21-6616-8115
% 		\end{itemize}
% \end{multicols}
% \end{itemize}



% \begin{itemize}
% 	\item \textbf{Nobahari, Hadi, PhD} \vspace{1pt}\\
% 	\textit{Professor of Aerospace Engineering, Sharif University of Technology}
% 	 \vspace{2pt}\\
% 	I have worked with Dr. Nobahari for over four years, including on both my master's and bachelor's theses.
% 	\begin{multicols}{2}
% 		\begin{itemize}
% 			\item \faGlobe \ \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Faculty Page at Sharif University}}
% 			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=vuUPY9kAAAAJ&hl=en&oi=ao}{\textcolor{blue}{Google Scholar Profile}}
% 			\item \faEnvelope \ \href{mailto:nobahari@sharif.edu}{nobahari@sharif.edu}
% 			\item \faPhone \ (+98)-21-6616-4040
% 		\end{itemize}
% \end{multicols}
% \end{itemize}




% \ifthenelse{\boolean{noshad}}
% {}
% {
% \begin{itemize}
% 	\item \textbf{Banazadeh, Afshin, PhD} \vspace{1pt}\\
% 	\textit{Professor of Aerospace Engineering, Sharif University of Technology}
% 	 \vspace{2pt}\\
% I have taken several courses with Dr. Banazadeh, achieving excellent results. I developed a fully designed regional jet and created a GUI to facilitate and automate the design process. Additionally, I served as a teaching assistant for the "Airplane Design II" course for one year.

% 	\begin{multicols}{2}
% 		\begin{itemize}
% 			\item \faGlobe \ \href{http://ae.sharif.edu/~portal/faculty/1014037799}{\textcolor{blue}{Faculty Page at Sharif University}}
% 			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=8Z6xyyUAAAAJ&hl=en}{\textcolor{blue}{Google Scholar Profile}}
% 			\item \faEnvelope \ \href{mailto:banazadeh@sharif.edu}{banazadeh@sharif.edu}
% 			\item \faPhone \ (+98)-21-6616-8108
% 		\end{itemize}
% \end{multicols}
% \end{itemize}
% }

% \vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PRESENTATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{center}
% 	{\noindent \bfseries PRESENTATIONS}
% \end{center}

% \vspace{8pt} % Gap between title and text

% \noindent
% {\bfseries [PRESENTER(s)]} {\itshape "[NAME OF PRSENTATION]"} Powerpoint Presentation. [CONFERENCE OR SYMPOSIUM NAME]. [LOCATION], [CITY], [STATE], USA. [YEAR]\\


% \vspace{0.2in} % Some whitespace between sections


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
