%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                          Curriculum Vitae Template Latex Code                  %
%                                                                                %
%                              Author: Manuel Pasqual Paul                       %
%                      Email: paul.manuel.pasqual@gmail.com                      %
%                                                                                %
%                             Last Edited: January 2020                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Specifications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{anysize}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{marvosym}
\usepackage{fontawesome5}
\usepackage[usenames,dvipsnames]{color}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Name & Contact Info %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\Large \bfseries Ali BaniAsad} \\ 
	{\large Curriculum Vitae} 	
\end{center}

	{\noindent \bf Contact Information} \\ 
	\href{mailto:alibaniasad1999@yahoo.com}{\faEnvelope} Email: \href{mailto:alibaniasad1999@yahoo.com}{alibaniasad1999@yahoo.com}   \\ 
	\faPhone \hspace{0pt}
	Phone: (+98) 991-214-7276  \\ 
	\href{https://linkedin.com/in/alibaniasad1999/}{\textcolor{blue}{\faLinkedin}}
	LinkedIn: \href{https://linkedin.com/in/alibaniasad1999/}{alibaniasad1999} \\
	\href{https://github.com/alibaniasad1999}{\faGithub}
	GitHub: \href{https://github.com/alibaniasad1999}{alibaniasad1999}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center} % Begin Text Centering
	{\noindent \bfseries EDUCATION}
\end{center} % End Text Centering

\vspace{8pt} % Gap between title and text

\noindent
 \bf{M.S.}
 \normalfont{Aerospace Engineering} \hfill Sep. 2022 -- Nov 2024 (Expected) \\ 
\noindent \textit{Sharif University of Technology} \\

\noindent
 \bf{B.S.}
\normalfont{Aerospace Engineering} \hfill Sep. 2017 -- May 2022 \\ 
\noindent \textit{Sharif University of Technology} \\
%{\setlength{\parindent}{1.1in} 
%	{\indent \sl \bfseries Honors} \\ 
%	\indent [HONOR ITEM] \\ 
%	\indent [HONOR ITEM]}
 
%\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTEREST %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{center}
% 	{\noindent \bfseries 1  2}
% \end{center}

% \vspace{8pt} % Gap between title and text
% \setlength{\parindent}{0.5in}

% \indent 
% [INSERT TEXT HERE] \\

% \vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH INTERSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries RESEARCH INTERESTS}
\end{center} 


\vspace{6pt}
\begin{multicols}{2} % Two-column layout
	\centering
\begin{itemize} % No \itemsep for tighter spacing
	\item \textbf{\noindent Robotics}
	\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
	    \item \textbf{Reinforcement Learning}
	    \begin{itemize} 
	        \item Multi-Agent Systems
	        \item Optimal Control in RL
	        \item Policy Optimization
	    \end{itemize}
	    \item \textbf{Computer Vision}
	    \begin{itemize} 
	        \item Object Detection
	        \item Sensor Fusion
	        \item Image Segmentation
	        \item 3D Reconstruction
	    \end{itemize}
	\end{itemize}
	\item \textbf{Artificial Intelligence}
	\begin{itemize} \itemsep -1pt
	    \item Machine Learning 
	    \item Artificial Neural Networks 
	    \item Deep Learning 
	    \item Natural Language Processing
	\end{itemize}
	\item \textbf{Control Systems}
	\begin{itemize} \itemsep -1pt
	    \item Optimal Control
	    \item Automatic Control
	    \item Robust Control
	\end{itemize}
	\item \textbf{Game Theory}
	\begin{itemize} \itemsep -1pt
	    \item Differential Game
	    \item Multi-Agent Game
	    \item Cooperative Game Theory
	    \item Non-Cooperative Game Theory
	\end{itemize}
\end{itemize}
\end{multicols}



\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MENTORING EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries PUBLICATIONS}
\end{center}

\vspace{8pt} % Gap between title and text


\noindent
{\bfseries Journal Papers}
\vspace{6pt}


\begin{itemize} \itemsep -2pt % Reduce space between items
	\item \textbf{Ali BaniAsad}, Alireza Sharifi, Reza Pordal, Hadi Nobahhari. "Attitude Control of a 3-DoF Quadrotor Platform Using a Linear Quadratic Integral Differential Game Approach." \textit{ISA Transactions, 
        \href{https://doi.org/10.1016/j.isatra.2024.03.005}{\textcolor{blue}{Elsevier}}}, 2024.
	\item Alireza Sharifi, \textbf{Ali BaniAsad}. "Robust In-Motion Transfer Alignment of Low-Grade Inertial Navigation Systems with Recurrent Neural Networks in the Event of Reference Malfunction." \textit{IEEE}, 2024 (Active)
	\item \textbf{Ali BaniAsad}, Hadi Nobahhari. "Robust Differential Game Reinforcement Learning with Soft Actor-Critic for Guidance in Low-Thrust Multi-Body Environments." \textit{AIAA}, 2024 (Active)
	% AHRS AI when there is no AI
	\item \textbf{Ali BaniAsad}, Alireza Sharifi. "Enhancing AHRS Results with Deep Learning LSTM Networks for Real-Time Attitude Estimation in GNSS-Denied Environments." \textit{Engineering Applications of Artificial Intelligence}, 2024 (Active) 
\end{itemize}

\vspace{0.2in} % Some whitespace between sections
\noindent
{\bfseries Conference Papers}

\vspace{6pt}
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Hadi Nobahhari,  \textbf{Ali BaniAsad}, Alireza Sharifi. "Linear Quadratic Integral Differential Game Applied to the Real-time Control of a Quadrotor Experimental Setup." \textit{ICRoM, \href{https://doi.org/10.1109/ICRoM57054.2022.10025263}{\textcolor{blue}{IEEE}}}, 2022.
\end{itemize}

\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROFESSIONAL EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries RESEARCH EXPERIENCE} % TODO: make it short
\end{center} 

\vspace{8pt} % Gap between title and text

\noindent
{\bfseries Researcher at
\href{https://www.linkedin.com/company/cnav-lab/}{\textcolor{blue}{CNAV Lab \faLinkedin}} \href{https://github.com/CNAVLAB}{\faGithub}
\textcolor{red}{
\href{https://youtube.com/@cnavlab?si=Fc-Y3oyKdgAmz3-5}{\faYoutube}}
} \hfill May 2020 -- Ongoing \\ 
\noindent \textit{Head of Lab (Current), Researcher (Former) }
\hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Hadi Nobahari, PhD} and
\href{https://ae.sharif.edu/~portal/faculty/1730782165}{Alireza Sharifi, PhD}

\begin{itemize} \itemsep -4pt % Reduce space between items
    \item Led projects focusing on the integration of embedded AI using C programming for the development of advanced robotic control systems, enhancing overall system efficiency and performance.
    \item Designed and implemented reinforcement learning (RL) algorithms to optimize robotic navigation and decision-making processes, significantly improving adaptability in dynamic environments.
    \item Developed advanced quadrotor technology with AI-driven navigation systems, including INS-AI and AHRS AI, resulting in enhanced precision, safety, and operational reliability during complex missions.
    \item Collaborated with interdisciplinary teams to integrate Robot Operating System (ROS) frameworks, streamlining development processes and ensuring effective communication across project stakeholders.
    \item Conducted rigorous testing and validation of AI navigation systems, utilizing real-world simulations to ensure robustness and reliability under various operational conditions.
\end{itemize}


\noindent
{\bfseries  Robust Reinforcement Learning Guidance
\href{https://github.com/CNAVLAB}{\faGithub}
} \hfill August 2022 -- November 2024 \\ 
\noindent \textit{Master's Thesis in Sharif University of Technology} \hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Hadi Nobahari, PhD}

\begin{itemize} \itemsep -4pt % Slightly reduced spacing for sub-items
	\item Investigated various reinforcement learning methods, comparing their performance to classic control strategies to identify advantages and limitations.
	\item Integrated Robot Operating System (ROS) to implement and test real-world robotic systems, validating performance in practical scenarios.
	\item Utilized differential game theory to develop robust and safe reinforcement learning algorithms, enhancing decision-making and trajectory planning in complex environments.
	\item Developed safety protocols and mechanisms to ensure reliable operation of robotic systems in uncertain conditions, focusing on minimizing risk during navigation and task execution.
	\item Conducted simulations to evaluate the robustness of the proposed methods, demonstrating their effectiveness in maintaining safety while optimizing performance under dynamic constraints.
\end{itemize}



\noindent
{\bfseries Game Theory-Based Control for a UAV 
\href{https://github.com/alibaniasad1999/bachelor-thesis}{\faGithub}
\textcolor{red}{
\href{https://youtu.be/SXZACxGaE1A?si=61yCRB8jFIZlldFG}{\faYoutube}}
} \hfill February 2021 -- September 2023 \\ 
\noindent \textit{Bachelor's Thesis in Sharif University of Technology} \hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Hadi Nobahari, PhD} 

\begin{itemize} \itemsep -4pt % Slightly reduced spacing for sub-items
    \item Developed a robust control system for a quadcopter using differential game theory, employing Nash equilibrium to optimize controller performance under uncertainty.
    \item Evaluated system performance through extensive Simulink simulations, ensuring the theoretical models translated effectively to real-world applications.
    \item Implemented and tested the control strategy on a three-degree-of-freedom setup, demonstrating the efficacy of the game-theoretic approach in practical scenarios.
    \item Conducted a series of experiments to assess the quadcopter's stability and responsiveness, refining the control algorithms based on performance feedback.
\end{itemize}



\noindent
{\bfseries Optimized Flocking of Autonomous Drones
\href{https://github.com/alibaniasad1999/Guidance-and-navigation}{\faGithub}
} \hfill July 2023 \\ 
\noindent \textit{Project in Sharif University of Technology} \hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Hadi Nobahari, PhD} 

\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
    \item Developed a UAV swarm model optimizing flocking behavior under real-world constraints, utilizing Embedded C for control algorithms and addressing challenges such as communication delays and environmental obstacles.
    \item Implemented and validated the model with Simulink simulations and Hardware-in-the-Loop (HIL) testing using a microcontroller, ensuring robustness and reliability in practical applications.
    \item Employed optimization techniques to enhance swarm performance, focusing on coordination and obstacle avoidance strategies.
\end{itemize}


\noindent
{\bfseries Multi-Objective Heuristic Optimization
\href{https://github.com/alibaniasad1999/Heuristic-optimization-algorithms}{\faGithub}
}
\hfill February 2023 \\ 
\noindent \textit{Project in Sharif University of Technology} \hfill Tehran, Iran \\
\noindent Supervisors: 
\href{https://ae.sharif.edu/~portal/faculty/1091235256}{Hadi Nobahari, PhD} 

\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
    \item Implemented the \href{https://link.springer.com/article/10.1007/s12652-022-04332-8}{\textcolor{blue}{REMARK}} algorithm for multi-objective optimization with conflicting objectives, allowing for the effective evaluation of trade-offs.
    \item Utilized heuristic methods to achieve high approximations of the Pareto set, balancing multiple objectives for optimal decision-making.
\end{itemize}


\noindent
{\bfseries Advanced Aircraft Trim Stability Analysis with DATCOM
\href{https://github.com/alibaniasad1999/DATCOM-Trim-Diagram-GUI}{\faGithub}
}
\hfill March 2022 \\ 
\noindent \textit{Project in Sharif University of Technology} \\ \hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{http://ae.sharif.edu/~portal/faculty/1014037799}{Afshin Banazadeh, PhD} 
\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
    \item Developed an advanced user interface (UI) for DATCOM software, streamlining the analysis workflow for aircraft trim stability assessments and enhancing user experience through intuitive design.
    \item Integrated features such as real-time data visualization and interactive parameter adjustments, allowing for more accurate and efficient evaluations of aircraft performance under various flight conditions.
    \item Conducted thorough testing and validation of the UI to ensure reliability and precision in output, significantly improving the design process for engineers and researchers.
\end{itemize}


\noindent
{\bfseries AIAA Regional Jet Design Competition
\href{https://github.com/alibaniasad1999/Airplane-Design-II}{\faGithub}
}
\hfill June 2021 \\ 
\noindent \textit{Project in Sharif University of Technology
% \href{https://github.com/alibaniasad1999/CV/blob/main/attachments/Phoenix%20Team-Modern%20Regional%20Jet.jpg}{Aircraft Design Poster}
} \hfill Tehran, Iran \\ 
\noindent Supervisors: 
\href{http://ae.sharif.edu/~portal/faculty/1014037799}{Afshin Banazadeh, PhD} 
\begin{itemize} \itemsep -1pt % Slightly reduced spacing for sub-items
    \item Led the comprehensive design of a regional jet, integrating various engineering disciplines to ensure optimal performance and compliance with industry standards.
    \item Utilized MATLAB and Python for complex computer modeling, including aerodynamic analysis, structural assessments, and performance simulations.
    \item Developed a detailed project report and presentation, showcasing design choices and simulation results, which facilitated a successful team presentation at the competition.
    \item Collaborated with a multidisciplinary team to refine design concepts, ensuring effective communication and integration of ideas throughout the project lifecycle.
\end{itemize}








\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%% VOLUNTEER EXPERIENCE & CAUSES %%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{center}
	{\noindent \bfseries TEACHING EXPERIENCE}
\end{center}
{\bfseries Teaching Assistant}
\begin{itemize}
	\item \noindent{\bfseries Fundamentals of Programming (C/C++)}
	 \hfill September 2018 -- December 2018 \\
	\textit{Department of Computer Engineering, Sharif University of Technology}\\
	%  \hfill [September 2017] \\ 
	\noindent Instructor: \href{https://www.linkedin.com/in/marjan-nikbin-a27451111}{\textcolor{blue}{Ms. Marjan Nikbin}}
	\item {\bfseries Automatic Control}
	 \hfill September 2021 -- Present \\
	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Hadi Nobahari}}, PhD and \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Alireza Sharifi}, PhD}
	\item {\bfseries Control Lab}
	 \hfill September 2021 -- Present \\
	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Hadi Nobahari}}, PhD and \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Alireza Sharifi}, PhD}
	\item {\bfseries Aircraft Design II}
	 \hfill September 2021 -- December 2021 \\
	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
	Instructors: \href{http://ae.sharif.edu/~portal/faculty/1014037799}{\textcolor{blue}{Afshin Banazadeh}} PhD
	\item {\bfseries Dynamics}
	 \hfill September 2021 -- December 2023 \\
	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Alireza Sharifi}}, PhD
	\item {\bfseries Introduction to Aerospace Engineering}
	 \hfill September 2021 -- December 2023 \\
	\textit{Department of Aerospace Engineering, Sharif University of Technology}\\
	Instructors: \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Alireza Sharifi}}, PhD


\end{itemize}




\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HONORS & MEMBERSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries AWARDS AND HONORS}
\end{center}

 
\vspace{8pt} % Gap between title and text


\noindent
{\bfseries Ranked 23} 
\hfill 2017 \vspace{4pt}\\
\textit{Ranked 23 among more than 6,000 participants in the Nationwide University Entrance Exam for Aerospace Engineering.}
% \vspace{12pt}
\vspace{04pt}

\noindent
{\bfseries Iranian Aerospace Society's Best Undergraduate Thesis Award} 
\hfill 2022 \vspace{4pt} \\
% TODO: add link
\textit{Awarded for the exceptional
undergraduate thesis titled "Control of a 3DOF Quadrotor Stand using a Linear-Quadratic-Integral Controller 
based on Differential Game Theory".}

\vspace{02pt}
\noindent
{\bfseries Ranked Top 0.5\%}\hfill 2017 \vspace{4pt} \\ 
\textit{Ranked Top 0.5\% among 150,000 participants of Iran's Undergraduate University Entrance Exam}

% \vspace{12pt}
% \noindent
% {\bfseries Admittance in the entrance exam of {\href{https://en.wikipedia.org/wiki/National_Organization_for_Development_of_Exceptional_Talents}{\textcolor{blue}{NODET}}} high school.}\hfill 2013 \\ 
% TODO: add link
% among 150,000 participants of Iran's Undergraduate University Entrance Exam



\vspace{0.2in} % Some whitespace between sections



\begin{center}
	{\noindent \bfseries TECHNICAL SKILLS}
\end{center}

% \begin{itemize}
% 	\small{\item{
% \textbf{Programming Languages}{: C/C++, Embedded C, MATLAB, Python \faPython} \\
% \textbf{Tools and Platforms}{: Git \faGit*, Linux \faLinux, ROS, Simulink, \faTerminal  Terminal,  \LaTeX} \\
% \textbf{Libraries/Frameworks}{: Matplotlib, NumPy, Pandas, PyTorch, TensorFlow} \\
% \textbf{Quantitative Skills}{: Artificial Neural Networks, Data Structures, Deep Learning, Embedded Machine Learning, Heuristic Optimization, Image Processing, Machine Learning, Optimization, Reinforcement Learning, Robotics}

% 			\textbf{Languages}{: Farsi (Native), English (Full Professional Proficiency)} \\
% 	}}
% \end{itemize}


% \begin{itemize}
%         \item \textbf{Programming Languages:} C/C++, Embedded C, MATLAB, 
% \end{itemize}

% Python \faPython \\
%         \textbf{Tools and Platforms:} Git \faGit, Linux \faLinux, ROS, Simulink, \faTerminal Terminal, \LaTeX \\
%         \textbf{Libraries/Frameworks:} Matplotlib, NumPy, Pandas, PyTorch, TensorFlow \\
%         \textbf{Quantitative Skills:} Artificial Neural Networks, Data Structures, Deep Learning, Embedded Machine Learning, Heuristic Optimization, Image Processing, Machine Learning, Optimization, Reinforcement Learning, Robotics \\
%         \textbf{Languages:} Farsi (Native), English (Full Professional Proficiency) 

\begin{itemize}
	\item \textbf{Programming Languages}
	\begin{multicols}{4}
		\begin{itemize}
			\item C/C++
			\item Embedded C
			\item MATLAB
			\item Python \faPython
		\end{itemize}
	\end{multicols}
	\item \textbf{Tools and Platforms}	
	\begin{multicols}{3}
		\begin{itemize}
			\item Git \faGitSquare
			\item Linux \faLinux
			\item ROS
			\item Simulink
			\item Terminal \faTerminal
			\item \LaTeX
		\end{itemize}
	\end{multicols}
	% \begin{itemize}
	% 	\item Git \faGit
	% 	\item Linux \faLinux
	% 	\item ROS
	% 	\item Simulink
	% 	\item Terminal \faTerminal
	% 	\item \LaTeX
	% \end{itemize}
	\item \textbf{Libraries/Frameworks:} 
	\begin{itemize}
		\item \textbf{Machine Learning Libraries:}
		\begin{multicols}{2}
			\begin{itemize}
				\item PyTorch
				\item TensorFlow
				\item Keras
				\item Scikit-learn
				\item OpenAI Gym
				\item JAX
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item PyTorch C and Python
		% 	\item TensorFlow C and Python
		% 	\item Keras
		% 	\item Scikit-learn
		% 	\item OpenAI Gym
		% \end{itemize}
	
		\item \textbf{Data Analysis and Visualization Libraries:}
		\begin{multicols}{4}
			\begin{itemize}
				\item Matplotlib
				\item NumPy
				\item Pandas
				\item OpenCV
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item Matplotlib
		% 	\item NumPy
		% 	\item Pandas
		% 	\item OpenCV
		% \end{itemize}
	
		\item \textbf{Simulation Tools:}
		\begin{multicols}{2}
			\begin{itemize}
				\item Gazebo
				\item MuJoCo
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item Gazebo
		% 	\item MuJoCo
		% \end{itemize}
	\end{itemize}
	\item \textbf{Robotics Skills}
	\begin{itemize}
		\item Machine Learning
		\begin{multicols}{2}
			\begin{itemize}
				\item Deep Learning
				\item Artificial Neural Networks
				\item Recurrent Neural Networks
				\item Embedded Machine Learning
				\item Reinforcement Learning
				\item Heuristic Optimization
				\item Convex Optimization
				\item Image Processing
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item Deep Learning
		% 	\item Artificial Neural Networks
		% 	\item Recurrent Neural Networks (RNN)
		% 	\item Embedded Machine Learning
		% 	\item Reinforcement Learning
		% 	\item Heuristic Optimization
		% 	\item Optimization
		% 	\item Image Processing
		% \end{itemize}
		\item Control Systems
		\begin{multicols}{3}
			\begin{itemize}
				\item Optimal Control
				\item Automatic Control
				\item Robust Control
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item Optimal Control
		% 	\item Automatic Control
		% 	\item Robust Control
		% \end{itemize}
		\item Game Theory
		\begin{multicols}{2}
			\begin{itemize}
				\item Differential Game
				\item Multi-Agent Systems
				\item Cooperative Game
				\item Non-Cooperative Game
			\end{itemize}
		\end{multicols}
		% \begin{itemize}
		% 	\item Game Theory
		% 	\item Differential Game Theory
		% 	\item Multi-Agent Systems
		% 	\item Multi-Agent Game
		% \end{itemize}
	\end{itemize}
	
	% \begin{itemize}
	% 	\begin{itemize}
	% 		\item Robotics
	% 	\end{itemize}	
	% \end{itemize}
	\item \textbf{Languages}
	\begin{itemize}
		\item Farsi (Native)
		\item English (Full Professional Proficiency) % add toefl score here 
		\vspace{1pt} \\ 
		The TOEFL iBT score is 96 (Reading: 26, Listening: 27, Speaking: 22, Writing: 21)  
		% very little arabic
	\end{itemize}
\end{itemize}

\vspace{0.2in} % Some whitespace between sections




\begin{center}
	{\noindent \bfseries NOTABLE COURSES}
\end{center}

\vspace{0.2in} % Some whitespace between sections

\noindent
{\bfseries University Courses} 
\hfill 2017 -- 2024\\
\textit{Sharif University of Technology, Tehran, Iran}
\begin{itemize}\itemsep -10pt
    \item \textbf{Programming and Computational Methods:}\vspace{-4pt}
    \begin{multicols}{2}\itemsep -4pt
    \begin{itemize}
        \item Basic Programming of C (20)
        \item Numerical Calculations (20)
    \end{itemize}
    \end{multicols}
    
    \item \textbf{Mathematics and Statistics:}\vspace{-4pt}
    \begin{multicols}{1}
    \begin{itemize}
        \item Engineering Mathematics (19.8)
        \item Probability and Statistics (20)
    \end{itemize}
    \end{multicols}
    
    \item \textbf{Control Systems:}\vspace{-4pt}
    \begin{multicols}{2}
    \begin{itemize}
        \item Automatic Control (18.1)
        \item Control Lab (18.5)
        \item Optimal Control (17.5)
    \end{itemize}
    \end{multicols}
    
    \item \textbf{Aerospace Engineering:}\vspace{-4pt}
    \begin{multicols}{2}
    \begin{itemize}
        \item Aircraft Design II (18.3)
        \item Flight Dynamics II (18.3)
    \end{itemize}
    \end{multicols}
    
    \item \textbf{Research and Projects:}\vspace{-4pt}
    \begin{multicols}{2}
    \begin{itemize}
        \item Bachelor Thesis (20)
    \end{itemize}
    \end{multicols}
\end{itemize}


\noindent
{\bfseries Online Courses} 
\hfill 2017 -- 2024\\

\begin{itemize} \itemsep -10pt
	\item \textbf{Robotics:} \\
	\textit{Provided by University of Pennsylvania, Courser} \hfill 
	\href{https://coursera.org/share/169250f50fb50f44b803162274217f86}{\textcolor{blue}{verify certificate}}
	\begin{multicols}{2}
		\begin{itemize}
			\item Aerial Robotics
			\item Computational Motion Planning
			\item Mobility
			\item Perception
			\item Estimation and Learning
			\item Capstone
		\end{itemize}
		\end{multicols}
	\item \textbf{Reinforcement Learning:} \\
	\textit{Provided by University of Alberta, Coursera} \hfill 
	\href{https://www.coursera.org/account/accomplishments/specialization/LWJMD8VB28PZ?utm_source=link&utm_medium=certificate&utm_content=cert_image&utm_campaign=sharing_cta&utm_product=s12n}{\textcolor{blue}{verify certificate}}
	% \begin{multicols}{1}
		\begin{itemize}
			\item Fundamentals of Reinforcement Learning
			\item Sample-based Learning Methods
			\item Prediction and Control with Function Approximation
			\item A Complete Reinforcement Learning System
		\end{itemize}
		\vspace{8pt}
		% \end{multicols}
	\item \textbf{IBM AI Engineering:} \\
	\textit{Provided by IBM, Coursera}
	\begin{itemize}
		\item Machine Learning with Python
		\item Introduction to Deep Learning and Neural Networks with Keras
		\item Building Deep Learning Models with TensorFlow
		\item Introduction to Neural Networks and PyTorch
		\item Introduction to Computer Vision and Image Processing
		\item AI Capstone Project with Deep Learning
	\end{itemize}
	\item \textbf{Neural Networks and Deep Learning:} \\
	\textit{Provided by deeplearning.ai, Coursera} \hfill
	\href{https://coursera.org/share/8d9110917e9443857718534087a51190}{\textcolor{blue}{verify certificate}}
	\vspace{8pt}
	\item \textbf{Python Data Structures:} \\
	\textit{Provided by University of Michigan, Coursera} \hfill
	\href{https://coursera.org/share/8944f2b056a3405c606e509e61f5570e}{\textcolor{blue}{verify certificate}}
	\vspace{8pt}
	\item \textbf{Introduction to Embedded Machine Learning:} \\
	\textit{Provided by Edge Impulse, Coursera} \hfill
	\href{https://coursera.org/share/0b709e9d6305db689ca5018f1531f4ef}{\textcolor{blue}{verify certificate}}
	\vspace{8pt}
	\item \textbf{Game Theory:} \\
	\textit{Provided by Stanford University, Coursera} \hfill
	\href{https://coursera.org/share/7c342a051890483df7748d65ad0113c2}{\textcolor{blue}{verify certificate}}
\end{itemize}





\begin{center}
	{\noindent \bfseries HOBBIES}
\end{center}
\begin{multicols}{3}
\begin{itemize} \itemsep -4pt
    \item Violin \faMusic
    \item Classical Music  \faHeadphones
    \item Reading  \faBook
    \item Coding  \faLaptopCode
    \item Swimming \faSwimmer
    \item Hiking \faMountain
    \item Traveling \faPlane
    \item Photography \faCamera
    \item Chess \faChess
\end{itemize}
\end{multicols}



\vspace{0.2in} % Some whitespace between sections



\begin{center}
	{\noindent \bfseries REFERENCES}
\end{center}
\begin{itemize}
	\item \textbf{Sharifi, Alireza, PhD} \\
	Assistant Professor of Aerospace Engineering, Sharif University of Technology \\
Dr. Sharifi Supervised my work in the \href{https://www.linkedin.com/company/cnav-lab/}{\textcolor{blue}{CNAV Lab}} for over three years, during which we collaborated on multiple projects.
I served as both a researcher and a teaching assistant during this time.
	\begin{multicols}{2}
		\begin{itemize}
			\item \faGlobe \ \href{https://ae.sharif.edu/~portal/faculty/1730782165}{\textcolor{blue}{Faculty Page at Sharif University}}
			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=k_OdlNMAAAAJ&hl=en}{\textcolor{blue}{Google Scholar Profile}}
			\item \faEnvelope \ \href{mailto:ar.sharifi@sharif.edu}{ar.sharifi@sharif.edu}
			\item \faPhone \ (+98)-21-6616-8115
		\end{itemize}
\end{multicols}
\end{itemize}



\begin{itemize}
	\item \textbf{Nobahari, Hadi, PhD} \vspace{1pt}\\
	\textit{Professor of Aerospace Engineering, Sharif University of Technology}
	 \vspace{2pt}\\
	I have worked with Dr. Nobahari for over four years, including on both my master's and bachelor's theses.
	\begin{multicols}{2}
		\begin{itemize}
			\item \faGlobe \ \href{https://ae.sharif.edu/~portal/faculty/1091235256}{\textcolor{blue}{Faculty Page at Sharif University}}
			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=vuUPY9kAAAAJ&hl=en&oi=ao}{\textcolor{blue}{Google Scholar Profile}}
			\item \faEnvelope \ \href{mailto:nobahari@sharif.edu}{nobahari@sharif.edu}
			\item \faPhone \ (+98)-21-6616-4040
		\end{itemize}
\end{multicols}
\end{itemize}





\begin{itemize}
	\item \textbf{Banazadeh, Afshin, PhD} \vspace{1pt}\\
	\textit{Professor of Aerospace Engineering, Sharif University of Technology}
	 \vspace{2pt}\\
I have taken several courses with Dr. Banazadeh, achieving excellent results. I developed a fully designed regional jet and created a GUI to facilitate and automate the design process. Additionally, I served as a teaching assistant for the "Airplane Design II" course for one year.

	\begin{multicols}{2}
		\begin{itemize}
			\item \faGlobe \ \href{http://ae.sharif.edu/~portal/faculty/1014037799}{\textcolor{blue}{Faculty Page at Sharif University}}
			\item \faGraduationCap \ \href{https://scholar.google.com/citations?user=8Z6xyyUAAAAJ&hl=en}{\textcolor{blue}{Google Scholar Profile}}
			\item \faEnvelope \ \href{mailto:banazadeh@sharif.edu}{banazadeh@sharif.edu}
			\item \faPhone \ (+98)-21-6616-8108
		\end{itemize}
\end{multicols}
\end{itemize}

% \vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PRESENTATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \begin{center}
% 	{\noindent \bfseries PRESENTATIONS}
% \end{center}

% \vspace{8pt} % Gap between title and text

% \noindent
% {\bfseries [PRESENTER(s)]} {\itshape "[NAME OF PRSENTATION]"} Powerpoint Presentation. [CONFERENCE OR SYMPOSIUM NAME]. [LOCATION], [CITY], [STATE], USA. [YEAR]\\


% \vspace{0.2in} % Some whitespace between sections


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}